---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dewi

<!-- badges: start -->
<!-- badges: end -->

The goal of dewi is to query German Wikitionary for a noun and its possible alternative forms. For example, querying the word "Japaner" (Male Japanese) will generate the plural form "Japaner", the genitiv form "Japaners", the dative plural form "Japanern", the female counterpart "Japanerin", the plural female counterpart "Japanerinnen".

## Installation

You can install the Github version of dewi with:

``` r
devtools::install_github("chainsawriot/dewi")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dewi)
dewi("Japaner")
```

```{r example2}
dewi("Japanerin")
```

```{r example3}
## N-deklination
dewi("Asiat")
```

```{r example4}
dewi("Erdbewohner")
```

```{r example5}
dewi("Frau")
```
