---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dewi

<!-- badges: start -->
[![R-CMD-check](https://github.com/chainsawriot/dewi/workflows/R-CMD-check/badge.svg)](https://github.com/chainsawriot/dewi/actions)
<!-- badges: end -->

The goal of dewi is to query German Wikitionary for a noun and its possible alternative forms. For example, querying the word "Japaner" (Male Japanese) will generate the plural form "Japaner", the genitive form "Japaners", the dative plural form "Japanern", the female counterpart "Japanerin", the plural female counterpart "Japanerinnen".

## Installation

You can install the Github version of dewi with:

``` r
devtools::install_github("chainsawriot/dewi")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r japaner}
library(dewi)
dewi("Japaner")
```

```{r japanerin}
dewi("Japanerin")
```

```{r asiat}
## N-deklination
dewi("Asiat")
```

```{r mannheimer}
dewi("Mannheimer")
```

Also useful for occupations, even weird ones.

```{r kowi}
dewi("Kommunikationswissenschaftler")
```


```{r re1}
dewi("Regierungschef")
```

```{r to1}
dewi("Tormann") %>% print(n = 100)
```

For nouns without an equivalent form in another gender, only the original form and its alternative forms will be returned.

```{r frau}
dewi("Frau")
```

The program returns `NA` if nothing is found.

```{r qwerty}
dewi("Qwerty")
```
